\documentclass[11pt]{resume}

\usepackage{fontspec}
\setmainfont{Liberation Sans}

\name{Vasilis Papavasileiou}

\address{Athens, Greece}
\address{\texttt{vasilis@fastmail.com}}
\address{\texttt{(+30)6988539039}}
\address{\texttt{https://github.com/vasilisp}}

\begin{document}

\begin{rSection}{Summary}
Backend engineer with a Ph.D. in Computer Science and a decade of
experience building large-scale, high-performance systems. Expert in
functional programming applied to real-world distributed systems,
delivering reliable, maintainable, and scalable solutions across
diverse technology stacks.
\end{rSection}

\begin{rSection}{Experience}

  \begin{rSubsection}{Ahrefs}{Jan 2019 -- Dec 2024}{Backend
      Developer}{Remote}
  \item Led development of one of the world’s largest Web crawlers,
    processing billions of pages per day.
  \item Built and maintained distributed OCaml backends for
    high-reliability, low-latency data processing.
  \item Developed petabyte-scale data pipelines and storage solutions
    using ClickHouse, RocksDB, and MySQL.
  \item Participated in DevOps for thousands of Linux hosts and
    multi-petabyte storage clusters.
  \end{rSubsection}

  \begin{rSubsection}{BeSport}{Jul 2017 -- Oct 2018}{Full-Stack
      Developer}{Paris, France}
  \item Developed and deployed social network features in OCaml,
    delivering production-ready code with strong guarantees on
    correctness.
  \item Created article classification algorithms improving content
    discovery and engagement.
  \item Continued core contributions to the Ocsigen Web Framework,
    enhancing reliability and developer productivity.
  \end{rSubsection}

  \begin{rSubsection}{Paris Diderot University}{Jun 2015 -- Jun
      2017}{Postdoctoral Researcher}{Paris, France}
  \item Maintained and extended the open-source Ocsigen Web Framework
    for OCaml.
  \item Developed a full-stack reactive programming framework to
    simplify client- and server-side page generation and updates.
  \item Implemented advanced type system features to ensure safe and
    robust client-server communication.
  \item Implemented a new high-performance HTTP backend adopted in
    production systems.
  \end{rSubsection}

\end{rSection}

\begin{rSection}{Education}

  \begin{rSubsection}{Northeastern University}{September 2009 -
      June 2015}{Ph.D. in Computer Science}{Boston, MA, USA}
  \item Dissertation: Mathematical Programming Modulo Theories
  \item Advisor: Pete Manolios
  \end{rSubsection}

  \begin{rSubsection}{National Technical University of Athens}{September 2003 -
      July 2009}{Diploma in Electrical and Computer
      Engineering}{Athens, Greece}
  \item Concentration: Computer Science
  \item Diploma Project: Program Verification with Coq
  \end{rSubsection}
	
\end{rSection}

\newpage

\begin{rSection}{Publications}

  \emph{Eliom: tierless Web programming from the ground up} \\
  Gabriel Radanne, Vasilis Papavasileiou, Jerome Vouillon, and Vincent
  Balat \\
  IFL, 2016 

  \emph{The Inez Mathematical Programming Modulo Theories Framework} \\
  Panagiotis Manolios, Jorge Pais, and Vasilis Papavasileiou \\
  CAV, 2015

  \emph{ILP Modulo Data} \\
  Panagiotis Manolios, Vasilis Papavasileiou, and Mirek Riedewald \\
  FMCAD, 2014

  \emph{ILP Modulo Theories} \\
  Panagiotis Manolios and Vasilis Papavasileiou \\
  CAV, 2013

  \emph{Pseudo-Boolean Solving by Incremental Translation to SAT} \\
  Panagiotis Manolios and Vasilis Papavasileiou \\
  FMCAD, 2011

  \emph{Synthesizing Cyber-Physical Architectural Models with Real-Time Constraints} \\
  Christine Hang, Panagiotis Manolios, and Vasilis Papavasileiou \\
  CAV, 2011

  \emph{Virtual Integration of CyberPhysical Systems by Verification} \\
  Panagiotis Manolios and Vasilis Papavasileiou \\
  AVICPS, 2010

\end{rSection}

\begin{rSection}{Academic Service}

  \begin{rSubsection}{Teaching Assistant}{2004 - 2013}{}{}
  \item Theory of Computation (Northeastern)
  \item Logic and Computation (Northeastern)
  \item Introduction to Programming (N.T.U. Athens)
  \end{rSubsection}

  \textbf{Conference Reviews} \hfill 2009-2015 % Bold company name and date to the right

  NFM (2015), FMCAD (2014, 2013, 2011), SAT (2014, 2012, 2011), CAV
  (2014, 2013), VSTTE (2013, 2012), DAC 2013, ITP 2011, TACAS 2011,
  DATE 2010

\end{rSection}

\begin{rSection}{Skills}

  \begin{tabular}{ll}
    Programming & OCaml, Go, C, C++, Python, Java, Common Lisp \\

    Databases & ClickHouse, PostgreSQL, MySQL, NoSQL (e.g., RocksDB) \\

    Other & Linux, DevOps, LLM technology, Formal Methods \\

    Languages & Greek, English, French (full professional
    proficiency), German (basic)
  \end{tabular}

\end{rSection}

\end{document}
